---
title: "Assessment3"
author: "John babu shaik s4606562 and Rueben Campbell s4626341"
date: "31/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Data Wrangling
#loading the libraries
```{r}

library(skimr)
library(scales)
library(tidyverse)

```

# loading the dataset
```{r}

fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

```

#By using skimr packages we can check the datatypes of all the columns in a dataset.
#Salads,x column can be removed from the data set as they are insignificant

```{r}
skim(fastfood)
summary(fastfood)

```

# converting the datatype of restaurant and salad column to factor and then showing the datatypes

```{r}
fastfood$restaurant<-as_factor(fastfood$restaurant)
fastfood$salad<-as_factor(fastfood$salad)
class(fastfood$restaurant)
class(fastfood$salad)
```
#replacing NA with 0 in the fastfood dataset.
```{r}
fastfood[is.na(fastfood)] <- 0
```

#cut_number creats n groups with the number of observations. 
#Creating a new variable caloies_type and saving it to the dataset and using cut_number function assigning labels and making them ordered results.
```{r}
fastfood<-fastfood%>%
  mutate(calories_type=cut_number(calories,3,
                                  labels=c("low","medium","high"),ordered_results=TRUE))
```

#creating a plot for calories_type in food items for each type of restaurant. Using facets and theme.
```{r}

ggplot(fastfood,aes(calories_type))+geom_bar()+facet_wrap(~restaurant)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#Another new variable created trans_fat_percentage is created to calculate the percentage of trans_fat and total_fat
```{r}
fastfood<-fastfood%>%
  mutate(trans_fat_percent = trans_fat/total_fat)
```

#creating a plot for rans_fat` in food items for each type of restaurant. Using facets and themes.
```{r}

  ggplot(fastfood,aes(trans_fat_percent))+geom_bar()+facet_wrap(~restaurant)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

#the average total_fat for each type of restaurant.

```{r}
fastfood%>%
  group_by(restaurant)%>%
  mutate(mean(total_fat))%>%
  summarise(total_fat=mean(total_fat))%>%
  ungroup()

```

#creating a plot that shows the comparision of different restaurants and mean(total_fat)
```{r}
fastfood%>%
  group_by(restaurant)%>%
  ggplot(aes(mean(total_fat)))+
  geom_bar()

```



